\thesistitle

### 2019-08-22 sections/results.tex
Finished up results

\begin{figure}[H]
  \includegraphics[width=1\textwidth]{img/maintainabilityscore}
  \caption{The effect of token volume on the delta maintainability score of the refactored system}
  \label{fig:maintainabilityscore}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=1\textwidth]{img/volume}
  \caption{The effect of token volume on the delta volume of the refactored system}
  \label{fig:volume}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=1\textwidth]{img/numberofparameters}
  \caption{The effect of token volume on the number of parameters of the refactored system}
  \label{fig:numberofparameters}
\end{figure}

In Figure~\ref{fig:complexity} we show the average delta complexity when clones with the specified token volume are refactored.

\begin{figure}[H]
  \includegraphics[width=1\textwidth]{img/complexity}
  \caption{The effect of token volume on the complexity of the refactored system}
  \label{fig:complexity}
\end{figure}

The volume of the clone is the dominating factor regarding the maintainability increase/decrease of cloned code. Because of that, for our further experiments, we filter out all refactorings with a token size smaller than 18 because otherwise the small clones dominate the results and turn all results towards unmaintainable.

>>>>

\begin{figure}[H]
  \includegraphics[width=1\textwidth]{img/maintainabilityscore}
  \caption{The effect of token volume on the delta maintainability score of the refactored clones}
  \label{fig:maintainabilityscore}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=1\textwidth]{img/volume}
  \caption{The effect of token volume on the delta volume of the refactored clones}
  \label{fig:volume}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=1\textwidth]{img/numberofparameters}
  \caption{The effect of token volume on the number of parameters of the refactored clones}
  \label{fig:numberofparameters}
\end{figure}

In Figure~\ref{fig:complexity} we show the average delta complexity when clones with the specified token volume are refactored. We did not add a trendline, as there does not seem to be a clear trend. The maximum delta complexity is 1, because the extracted method itself has a complexity of 1. For each branching point in the cloned fragment, the complexity of the system will decrease when such a clone is refactored.

\begin{figure}[H]
  \includegraphics[width=1\textwidth]{img/complexity}
  \caption{The effect of token volume on the complexity of the refactored clones}
  \label{fig:complexity}
\end{figure}

The volume of the clone is the dominating factor regarding the maintainability increase/decrease of cloned code. Because of that, in our further experiments we filter out all refactorings with a token size smaller than 18 because otherwise the small clones dominate the results and turn all results towards unmaintainable.
